---
title: "Live Core Regression Reproduction"
author: "Barnby, J.M."
date: "02/09/2021"
output: 
  prettydoc::html_pretty:
    theme: architect
    highlight: github
    math: katex
---

## Introduction

This rmd is intended to act as a live script to process all of the core regression and summary statistics reported in Barnby et al., 2021.

Click each chunk to see a live reproduction of the results reported.

## Library load

```{r library, message = F, error = F, warning = F}

library(tidyverse)
library(psych)
library(ggrepel)
library(R.matlab)
library(dunn.test)

source("Analysis/Functions.R")
source("Analysis/Phase1SimulationR.R")
```

## Data load

```{r data}

ControlDF         <- read.csv('Data/ControlDF.csv') # main df
Intentions_choice <- read.csv("Data/Intentions_Phase1.csv") # choice sets
Intentions_guess  <- read.csv("Data/Intentions_Phase2.csv") # choice sets
RecData           <- readMat('Modelling/Fit_CBM/hbi_models3.mat') # fitted hierarchical parms
```

## Summary Statistics

```{r summary}

summstat <- rbind(
psych::describe(ControlDF$Persec),
psych::describe(ControlDF$ICARTot)
)

rownames(summstat) <- c('Paranoia', 'ICAR')
summstat

```

## Behavioral Analysis

### Phase 1

```{r behav_phase1, echo=FALSE, message = F, error = F, warning = F}

Intentions_choice %>%
    mutate(Prosocial=ifelse(ChoiceAction == 1, 1, 0),
           Individualistic=ifelse(ChoiceAction == 2, 1, 0),
           Competitive=ifelse(ChoiceAction == 3, 1, 0)) -> choice_alt

choice_alt %>%
  group_by(id) %>%
  mutate(Type1  = ifelse(Type1 == 'Competative', 'Competitive', Type1),
         Type2  = ifelse(Type2 == 'Competative', 'Competitive', Type2),
         Choice  = ifelse(Choice == 'Competative', 'Competitive', Choice),
         pairPI = ifelse((Type1 == 'Prosocial'   & Type2 == 'Individual'  | Type1 == 'Individual'  & Type2 == 'Prosocial'  ) & Choice == 'Prosocial', 1, 0),
         pairCI = ifelse((Type1 == 'Competitive' & Type2 == 'Individual'  | Type1 == 'Individual'  & Type2 == 'Competitive') & Choice == 'Individual', 1, 0),
         pairPC = ifelse((Type1 == 'Prosocial'   & Type2 == 'Competitive' | Type1 == 'Competitive' & Type2 == 'Prosocial'  ) & Choice == 'Prosocial', 1, 0),
         sumPI = sum(pairPI)/6,
         sumCI = sum(pairCI)/6,
         sumPC = sum(pairPC)/6) %>%
  as.data.frame() -> pairComparisons

pairComparisons %>%
  pivot_longer(sumPI:sumPC, 'pair', 'value') %>%
  group_by(pair) %>%
  summarise(sd = sd(value)*100, value = mean(value)*100)
```

```{r Prosocial-Individualist, message = F, error = F, warning = F}
model.compare(lm(scale(sumPI) ~ scale(Persec) + scale(ICARTot) + Age + Sex + Control, data = pairComparisons, na.action = na.fail))
```

```{r Individualist-Competitive, message = F, error = F, warning = F}
model.compare(lm(scale(sumCI) ~ scale(Persec) + scale(ICARTot) + Age + Sex + Control, data = pairComparisons, na.action = na.fail))
```

```{r Prosocial-Competitive, message = F, error = F, warning = F}
#model.compare(lm(scale(sumPC) ~ scale(Persec) + scale(ICARTot) + Age + Sex + Control, data = pairComparisons, na.action = na.fail))
summary(lm(scale(sumPC) ~ scale(Persec) + scale(ICARTot) + Age + Sex + Control, data = pairComparisons, na.action = na.fail))
confint(lm(scale(sumPC) ~ scale(Persec) + scale(ICARTot) + Age + Sex + Control, data = pairComparisons, na.action = na.fail))
```

### Phase 2

#### Accuracy

```{r behav_phase2, echo=FALSE, message = F, error = F, warning = F}

ControlDF %>%
  group_by(PartnerPolicy) %>%
  summarise(mean = mean(Sum), sd = sd(Sum))
```

```{r Overall, message = F, error = F, warning = F}
#To assess partner policy influence
ControlDFMod1 <- ControlDF %>%
  mutate(PartnerPolicy = factor(PartnerPolicy, levels = c('Prosocial', 'Individualist', 'Competitive')))
model.compare(lm(scale(Sum) ~ PartnerPolicy + #behavioural analysis
                   scale(Persec) + scale(ICARTot) + scale(Age) + Sex + Control,
                 data = ControlDFMod1,
                 na.action = na.fail))

#change factor level to add different contrasts
ControlDFMod2 <- ControlDF %>%
  mutate(PartnerPolicy = factor(PartnerPolicy, levels = c('Individualist', 'Competitive', 'Prosocial'))) # change factor levels for adjusted analysis
model.compare(lm(scale(Sum) ~ PartnerPolicy + #behavioural analysis
                   scale(Persec) + scale(ICARTot) + scale(Age) + Sex + Control,
                 data = ControlDFMod2,
                 na.action = na.fail))
```

```{r Paranoia and general cognition, message = F, error = F, warning = F}
#to assess paranoia and general cognition on accuracy
model.compare(lm(scale(Sum) ~ scale(Persec) + scale(ICARTot) + scale(Age) + Sex + Control,
                 data = ControlDF,
                 na.action = na.fail))
```

#### Partner Classification

```{r, warning = F, error = F, message=F}

Intentions_guess %>%
  group_by(PartnerPolicy) %>%
  filter(Trial == 36, Final_Guess != 'Please select an option') %>%
  distinct() %>%
  count(Final_Guess)

Intentions_guess %>%
  group_by(PartnerPolicy) %>%
  filter(Trial == 36, Final_Guess != 'Please select an option') %>%
  mutate(Final_Guess = case_when(
    Final_Guess == 'Trying to earn as much money as possible' ~ 2,
    Final_Guess == 'Trying to share as much money between us as possibe' ~ 1,
    Final_Guess == 'Trying to stop me from earning points' ~ 3 
  )) %>%
  distinct() -> modelExplicit

modelExplicit_P <- modelExplicit %>% filter(PartnerPolicy == 'Prosocial')
modelExplicit_I <- modelExplicit %>% filter(PartnerPolicy == 'Individualist')
modelExplicit_C <- modelExplicit %>% filter(PartnerPolicy == 'Competative')

kruskal.test(modelExplicit_P$Persec, modelExplicit_P$Final_Guess)
dunn.test(modelExplicit_P$Persec, modelExplicit_P$Final_Guess, method = 'BH')
kruskal.test(modelExplicit_I$Persec, modelExplicit_I$Final_Guess)
kruskal.test(modelExplicit_C$Persec, modelExplicit_C$Final_Guess)

```

#### Intent Attributions

```{r intent_behav_overall, message = F, error = F, warning = F}

model.compare(lm(scale(HI) ~ scale(Sum) + scale(Persec) + PartnerPolicy + scale(ICARTot) + Age + Sex + Control,
           data = ControlDFMod1,
           na.action = na.fail))

model.compare(lm(scale(SI) ~ scale(Sum) + scale(Persec) + PartnerPolicy + scale(ICARTot) + Age + Sex + Control,
           data = ControlDFMod1,
           na.action = na.fail))
```

```{r intent_behav_withinsubjs, message = F, error = F, warning = F}

#Within partner analysis
model.compare(lm(scale(HI) ~ scale(Sum) + scale(Persec) + scale(ICARTot) + Age + Sex + Control,
           data = data1P,
           na.action = na.fail))
model.compare(lm(scale(HI) ~ scale(Sum) + scale(Persec) + scale(ICARTot) + Age + Sex + Control,
           data = data1I,
           na.action = na.fail))
model.compare(lm(scale(HI) ~ scale(Sum) + scale(Persec) + scale(ICARTot) + Age + Sex + Control,
           data = data1C,
           na.action = na.fail))

model.compare(lm(scale(SI) ~ scale(Sum) + scale(Persec) + scale(ICARTot) + Age + Sex + Control,
           data = data1P,
           na.action = na.fail))
model.compare(lm(scale(SI) ~ scale(Sum) + scale(Persec) + scale(ICARTot) + Age + Sex + Control,
           data = data1I,
           na.action = na.fail))
model.compare(lm(scale(SI) ~ scale(Sum) + scale(Persec) + scale(ICARTot) + Age + Sex + Control,
           data = data1C,
           na.action = na.fail))

```

## Computational Analysis

### Phase 1

```{r compu_phase1_hierarchical, warning = F, message = F}

#Hierarchical means
1/(1+exp(-RecData$cbm[,,1]$output[,,1]$group.mean[[1]][[1]][,1]))*15
RecData$cbm[,,1]$output[,,1]$group.mean[[1]][[1]][,2]

#Hierarchical error bars
RecData$cbm[,,1]$output[,,1]$group.hierarchical.errorbar[[1]][[1]][,1]
RecData$cbm[,,1]$output[,,1]$group.hierarchical.errorbar[[1]][[1]][,2]

```

```{r compu_phase1_centraltends, warning=F, message=F, error=F}


model.compare(lm(scale(alpha_m) ~ scale(beta_m) + scale(ICARTot) + scale(Persec) + scale(Age) + Sex + Control,
                 data =ControlDF,
                 na.action = na.fail))

model.compare(lm(scale(beta_m) ~ scale(alpha_m) + scale(ICARTot) + scale(Persec) + scale(Age) + Sex + Control,
                 data =ControlDF,
                 na.action = na.fail))


```

### Phase 2

#### Accuracy

Overall model

```{r compu_phase2_overall_accuracy, warning=F, message=F, error=F}

#Overall accuracy
model.compare(lm(scale(Sum) ~ scale(alpha_v) * scale(beta_v) * scale(ProbFix) +
                   scale(Persec) + scale(ICARTot) + scale(Age) + Sex + Control,
                 data = ControlDF,
                 na.action = na.fail))

#Persecutory Ideation by parameters and covariates
model.compare(lm(scale(Persec) ~ scale(alpha_v) * scale(beta_v) * scale(ProbFix)+
                   scale(ICARTot) + scale(Age) + Sex + Control,
                 data = ControlDF,
                 na.action = na.fail))

#ICAR by parameters and covariates
model.compare(lm(scale(ICARTot) ~ scale(alpha_v) * scale(beta_v) * scale(ProbFix)+
                   scale(Persec) + scale(Age) + Sex + Control,
                 data =ControlDF,
                 na.action = na.fail))
```

Post-hoc exploration

```{r compu_phase2_accuracy, warning=F, message=F, error=F}

#Layer1
l1 <- lm(scale(Sum) ~ scale(ICARTot) + Age + Sex + Control,
                 data = ControlDF,
                 na.action = na.fail)
summary(l1)
#Layer 2
l2 <- lm(scale(Sum) ~ scale(Persec) + scale(ICARTot) + Age + Sex + Control,
                 data = ControlDF,
                 na.action = na.fail)
summary(l2)
#Layer 3
l3 <- lm(scale(Sum) ~ scale(ProbFix) + scale(Persec) + scale(ICARTot) + Age + Sex + Control,
           data = ControlDF,
           na.action = na.fail)
summary(l3)
#Layer 4
l4      <- lm(scale(Sum) ~ scale(alpha_v) + scale(beta_v) + scale(ProbFix) + scale(Persec) + scale(ICARTot) + Age + Sex + Control,
                    data = ControlDF,
                    na.action = na.fail)
summary(l4)
#Layer 5
l5      <- lm(scale(Sum) ~ scale(ProbFix) * scale(alpha_v) * scale(beta_v) + scale(Persec) + scale(ICARTot) + Age + Sex + Control,
           data = ControlDF,
           na.action = na.fail)
summary(l5)
confint(l5)
```

#### Intention Attributions

Overall model

```{r compu_phase2_overall_intent, warning=F, message=F, error=F}

model.compare(lm(scale(HI) ~ scale(alpha_v) + scale(beta_v) + scale(ProbFix) + scale(Sum) +
      PartnerPolicy + scale(Persec) + scale(ICARTot) + scale(Age) + Sex + Control,
                 data = ControlDF,
                 na.action = na.fail))

model.compare(lm(scale(SI) ~ scale(alpha_v) + scale(beta_v) + scale(ProbFix) + scale(Sum) +
      PartnerPolicy + scale(Persec) + scale(ICARTot) + scale(Age) + Sex + Control,
                 data = ControlDF,
                 na.action = na.fail))
```

Post-hoc exploration

```{r compu_phase2_within_intent, warning=F, message=F, error=F}

#Harmful Intent

#Layer1
l1HI <- lm(scale(HI) ~ scale(ICARTot) + PartnerPolicy + Age + Sex + Control,
                 data = ControlDF,
                 na.action = na.fail)
summary(l1HI)
#Layer 2
l2HI <- lm(scale(HI) ~ scale(Sum) + PartnerPolicy + scale(ICARTot) + Age + Sex + Control,
                 data = ControlDF,
                 na.action = na.fail)
summary(l2HI)
#Layer 3
l3HI <- lm(scale(HI) ~ scale(Persec) + scale(Sum) + PartnerPolicy + scale(ICARTot) + Age + Sex + Control,
           data = ControlDF,
           na.action = na.fail)
summary(l3HI)

#Layer 4
l4HI <- lm(scale(HI) ~ scale(ProbFix) + scale(Persec) + scale(Sum) + PartnerPolicy + scale(ICARTot) + Age + Sex + Control,
           data = ControlDF,
           na.action = na.fail)
summary(l4HI)

#Layer 5
l5HI <- lm(scale(HI) ~ scale(alpha_v) + scale(beta_v) + scale(ProbFix) + scale(Persec) + scale(Sum) + PartnerPolicy + scale(ICARTot) + Age + Sex + Control,
           data = ControlDF,
           na.action = na.fail)
summary(l5HI)

#Self Interest

#Layer1
l1SI <- lm(scale(SI) ~ scale(ICARTot) + PartnerPolicy + Age + Sex + Control,
                 data = ControlDF,
                 na.action = na.fail)
summary(l1SI)
#Layer 2
l2SI <- lm(scale(SI) ~ scale(Sum) + PartnerPolicy + scale(ICARTot) + Age + Sex + Control,
                 data = ControlDF,
                 na.action = na.fail)
summary(l2SI)
#Layer 3
l3SI <- lm(scale(SI) ~ scale(Persec) + scale(Sum) + PartnerPolicy + scale(ICARTot) + Age + Sex + Control,
           data = ControlDF,
           na.action = na.fail)
summary(l3SI)

#Layer 4
l4SI <- lm(scale(SI) ~ scale(ProbFix) + scale(Persec) + scale(Sum) + PartnerPolicy + scale(ICARTot) + Age + Sex + Control,
           data = ControlDF,
           na.action = na.fail)
summary(l4SI)

#Layer 5
l5SI <- lm(scale(SI) ~ scale(alpha_v) + scale(beta_v) + scale(ProbFix) + scale(Persec) + scale(Sum) + PartnerPolicy + scale(ICARTot) + Age + Sex + Control,
           data = ControlDF,
           na.action = na.fail)
summary(l5SI)

```

#### 
